Parsing Postfix log files

### 2009-02-13 doc/logparser-implementation.tex
Fixed some 'overfull hbox' problems.

    \item [connection\_data] Sometimes rules need to save data that is not
        present in the log line: e.g.\ setting \texttt{client\_ip} when a
        mail is being delivered to another server.  The format is:
        \newline{} \tab{} \texttt{ client\_hostname = localhost, client\_ip
        = 127.0.0.1} \newline{} i.e.\ semi-colon or comma separated
        assignment statements, with the variable name on the left and the
        value on the right hand side.\footnote{Commas and semi-colons
        cannot be escaped and thus cannot be used.  This feature is
        intended for use with small amounts of data rather than large
        amounts in any one rule, so dealing with escape sequences was
        deemed unnecessary.}  Any field in the connections table can be set
        in this way.

@@

\subsection{Bounce Notification Mails Delivered Before Their Creation Is
Logged}

>>>>

    \item [connection\_data] Sometimes rules need to save data that is not
        present in the log line: e.g.\ setting \texttt{client\_ip} when a
        mail is being delivered to another server.  The format is:
        \newline{} \tab{} \texttt{ client\_hostname = localhost,}
        \newline{} \tab{} \tab{} \texttt{client\_ip
        = 127.0.0.1} \newline{} i.e.\ semi-colon or comma separated
        assignment statements, with the variable name on the left and the
        value on the right hand side.\footnote{Commas and semi-colons
        cannot be escaped and thus cannot be used.  This feature is
        intended for use with small amounts of data rather than large
        amounts in any one rule, so dealing with escape sequences was
        deemed unnecessary.}  Any field in the connections table can be set
        in this way.

@@

\subsection{Bounce Notification Mails Are Delivered Before Their Creation
Is Logged}

### 2009-02-13 doc/logparser-results.tex
Fixed some 'overfull hbox' problems.

    \item [optimal]  The most optimal order, according to the hypothesis:
        rules that match most often will be tried first.

    \item [shuffle] This is intended to represent a randomly ordered rule
        set.  The rules will be shuffled once before use and will retain
        that ordering until the parser exits.  Note that the ordering will
        change every time the parser is executed, so 10 different rule
        orderings will be generated for each log file in the test run.

    \item [reverse] Hypothetically the worst order: the most frequently
        matching rules will be tried last.

>>>>

    \item [Optimal]  The most optimal order, according to the hypothesis:
        rules that match most often will be tried first.

    \item [Shuffle] This is intended to represent a randomly ordered rule
        set.  The rules will be shuffled once before use and will retain
        that ordering until the parser exits.  Note that the ordering will
        change every time the parser is executed, so 10 different rule
        orderings will be generated for each log file in the test run.

    \item [Reverse] Hypothetically the worst order: the most frequently
        matching rules will be tried last.
